---
title: "R final"
output: html_document
date: "2022-12-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(RColorBrewer)
library(ggplot2)
```
## IMPORTING THE DATASET
```{r}
Electric_Vehicle_Population_Data <- read_csv("R assignment/Electric Vehicle Population Data.csv")
```





## DATASET CLEANING TO REMOVE ALL NULL VALUES.
```{r}
Electric_Vehicle_Population_Data %>%
  select(VIN, County, City, State, ZIP_Code, Model_Year, Make, Model, Electric_Vehicle_Type, CAFV, Range_Km, Base_MSRP, Legislative_District, DOLVehicleID, VehicleLocation, ElectricUtility) %>% na.omit()
```
## CHECKING FOR NULL VALUES IN DATASET.
```{r}
is.null(Electric_Vehicle_Population_Data)
```
## TO CHECK THE COUNT OF CITIES.
```{r}
table(Electric_Vehicle_Population_Data["City"])
```
## TO CHECK THE COUNT OF MAKE{BRANDS}.
```{r}
table(Electric_Vehicle_Population_Data["Make"])
```



## CALCULATE THE COUNT OF ELECTRIC VEHICLE TYPE{BEV/PHEV} PER CITY AND ARRANGING IN DECREASING ORDER.
```{r}
NEW_TABLE <- Electric_Vehicle_Population_Data %>% count(City , Electric_Vehicle_Type , sort = TRUE)
NEW_TABLE
```
## CALCULATE THE COUNT OF MAKE{BRAND} AND ELECTRIC VEHICLE TYPE{BEV/PHEV} PER STATE AND ARRANGING IN DECREASING ORDER.
```{r}
NEW_TABLE2 <- Electric_Vehicle_Population_Data %>% count(State , Make , Electric_Vehicle_Type,  sort = TRUE)
NEW_TABLE2
```
## CALCULATE THE COUNT OF MAKE{BRAND} AND ELECTRIC VEHICLE TYPE{BEV/PHEV} PER YEAR AND ARRANGING IN DECREASING ORDER.
```{r}
NEW_TABLE3 <- Electric_Vehicle_Population_Data %>% count(Model_Year , Make, Electric_Vehicle_Type , sort = TRUE)
NEW_TABLE3
```
## ## CALCULATE THE COUNT OF INDIVIDUAL MAKE{BRAND} PER CITY WITH RESPECT TO ITS MODEL YEAR AND ARRANGING IN DECREASING ORDER.
```{r}
NEW_TABLE4 <- Electric_Vehicle_Population_Data %>% count(City , Make, Model_Year, sort = TRUE)
NEW_TABLE4
```




## TO SHOW THE PREFERENCE OF ELECTRIC VEHICLE TYPE{BEV/PHEV} IN CITIES AND TAKING THE TOP 20 COUNT. 
```{r}
NEW_TABLE %>%
  slice(1:20) %>%
ggplot(., aes(x = City, y = n, color = Electric_Vehicle_Type)) + 
  geom_bar(stat = 'identity') +
labs(title ="ELECTRIC VEHICLE TYPE PER CITY")  + 
  theme(axis.text.x=element_text(angle = -90, hjust = 0))
```
## TO SHOW WHICH MAKE{BRANDS} INCREASED THE PRODUCTION OF ELECTRIC VEHICLE TYPE{BEV/PHEV} PER YEAR.
```{r}
ggplot(data = NEW_TABLE3, mapping = aes(x = Make, y= Model_Year, size = n, color = Electric_Vehicle_Type))+
geom_point() +
labs(title = "Electric Vehicles type increase per Brand with respect to year ") +
  theme(axis.text.x=element_text(angle = -90, hjust = 0))
 
```
## TO SHOW THE PREFERENCE OF MAKE{BRANDS} AND ELECTRIC VEHICLE TYPE{BEV/PHEV} IN EACH STATE.
```{r}
ggplot(NEW_TABLE2, aes(Electric_Vehicle_Type, State, color = Make, size = Year)) +
  geom_boxplot(size = 1) +
  labs(title = "Statewise increase in Electric Vehicles Type with respect to Brand " )
```
## TO SHOW TOP PREFERED ELECTRIC VEHICLE MANUFACTURING MAKE{BRANDS} IN TOP 40 CITIE PER YEAR.
```{r}
NEW_TABLE4 %>%
  slice(1:40) %>%
ggplot(., mapping = aes(x = City, y = n, color = Make)) +
geom_point() +
facet_wrap(~ Model_Year) +
  labs(title = "Top Electric Vehicle Manufacturing Companies From 2013 to 2022" ) +
   theme(axis.text.x=element_text(angle = -90, hjust = 0))

```
## AS TESLA IS THE MOST PREFERED ELECTRIC VEHICLE MANUFACTURING BRAND AND BATTERY ELECTRIC VEHICLE ARE THE MOST PREFERED ELECTRIC VEHICLE TYPE ACCORDING TO THIS ANALYSIS, 
## TO CHECK WEATHER TESLA HAS THE MOST BATTERY ELECTRIC VEHICLE CARS.
```{r}
TABLE_CHECK <- Electric_Vehicle_Population_Data %>% count(Make, Electric_Vehicle_Type, sort = TRUE)
TABLE_CHECK
```




